Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-14 journal paper/content/sec-bg.tex
Revised some appendix titles.
Copied stuff from body.

>>>>

Let us connect \BIR with the three classes of algorithms listed in Section~\ref{sec:intro-model}. \DynGreedy has at least a constant \BIR for many reasonable priors (where the constant can depend on $K$ and the prior, but not on $n$). \StaticGreedy typically has at least a constant \BIR, in the same sense. Exploration-separating algorithms can have
    $\BIR(n) \sim n^{-1/3}$
for all priors, whereas adaptive-exploration algorithms can have an even better rate
    $\BIR(n) \sim n^{-1/3}$
for all priors. Both rates are up to $\log(n)$ factors, and are the best possible \BIR rates that can be achieved for all priors. More details on this can be found in Appendix~\ref{app:examples}.
